\pkg{evtree}: Evolutionary Learning of Globally Optimal Classification and Regression Trees in \proglang{R}

### 2011-11-11 pkg/evtree/inst/doc/evtree.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@271 255f4249-2263-4417-b1ea-8498779e27a7

In the following, a binary tree model with $M$ terminal nodes (which consequently has
$M-1$ internal splits) is denoted by
%
\begin{equation}
  \theta ~=~ (v_{n_1}, s_{n_1},...,v_{n_{M-1}},s_{n_{M-1}} ), \label{eq:tree}
\end{equation}
%
where the $n_r \in \{1,...,M_{\max}-1\}$ are the positions of the
internal \emph{nodes}, $v_r \in \{1, \dots ,P\}$ the associated splitting
\emph{variables}, and $s_r$ the associated \emph{split} rules ($r = 1, \dots, M-1$).
Depending on the domain of $X_{v_r}$, the split rule $s_r$ contains either a cutoff
(for ordered and numeric variables) or a a nonempty subset of $\{1, \dots, c\}$
(for a categorical variable with $c$~levels), determining which observations are
sent to the first or second subsample. In the former case, there are $u-1$ possible
split rules if $X_{v_r}$ takes $u$ distinct values; and in the latter case, there
are $2^{c-1} - 1$ possible splits. Thus, the product of all of these combinations
forms all potential elements $\theta$ from $\Theta_M$, the space of conceivable
trees with $M$ terminal nodes. The overall parameter space is then 
$\Theta =\bigcup_{M=1}^{M_{\max}} \Theta_{M}$ (which in practice is often reduced
by exluding elements $\theta$ resulting in too small subsamples etc.).

>>>>

In the following, a binary tree model with $M$ terminal nodes (which consequently has
$M-1$ internal splits) is denoted by
%
\begin{equation}
  \theta ~=~ (v_{n_1}, s_{n_1},...,v_{n_{M-1}},s_{n_{M-1}} ), \label{eq:tree}
\end{equation}
%
where the $n_r \in \{1,...,M_{\max}-1\}$ are the positions of the
internal \emph{nodes}, $v_r \in \{1, \dots ,P\}$ the associated splitting
\emph{variables}, and $s_r$ the associated \emph{split} rules ($r = 1, \dots, M-1$).
Depending on the domain of $X_{v_r}$, the split rule $s_r$ contains either a cutoff
(for ordered and numeric variables) or a nonempty subset of $\{1, \dots, c\}$
(for a categorical variable with $c$~levels), determining which observations are
sent to the first or second subsample. In the former case, there are $u-1$ possible
split rules if $X_{v_r}$ takes $u$ distinct values; and in the latter case, there
are $2^{c-1} - 1$ possible splits. Thus, the product of all of these combinations
forms all potential elements $\theta$ from $\Theta_M$, the space of conceivable
trees with $M$ terminal nodes. The overall parameter space is then 
$\Theta =\bigcup_{M=1}^{M_{\max}} \Theta_{M}$ (which in practice is often reduced
by exluding elements $\theta$ resulting in too small subsamples etc.).
